---
title: "qclc-guide"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{qclc-guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Workflow Overview for MA and EWMA Analysis

This workflow demonstrates the process for conducting quality control chart analysis using Moving Average (MA) and Exponentially Weighted Moving Average (EWMA) methods.

1. **Control Parameter Calculation**:
   The initial step involves calculating control parameters such as the process mean (`mu`) and variance (`sigma2`), which are critical for establishing control limits.

2. **Simulations for In-Control Process**:
   Simulations are run using the control parameters to estimate the Average Run Length (ARL) and false positive (FP) rates for an in-control process (scenario 0). This step helps to determine the expected number of observations before a false alarm occurs under normal conditions.

3. **Simulations for Out-of-Control Process**:
   To assess the detection capability of the charts, additional simulations are conducted with a shifted process mean. This calculates the ARL and true positive (TP) rates for an out-of-control process (scenario 1), providing insight into the charts' sensitivity to process deviations.

4. **MA and EWMA Statistic Computation**:
   The `ma_statistic()` and `ewma_statistic()` functions are used to compute the moving average and exponentially weighted moving average statistics for monitoring process behavior.

5. **Upper and Lower Control Limits**:
   Upper and lower control limits for MA and EWMA charts are determined to visualize the boundaries within which the process is expected to operate under normal conditions.

```{r setup}
library(qclc)

set.seed(1234)
x = rnorm(100)
```

## Moving Average (MA)

### MA Control Parameters

```{r}
aux <- control_parm_ma(x, omega = 10)
```

### MA - Process Under Control (scenario 0)

```{r}
arl_ma(x, mu = aux$mu, sigma2 = aux$sigma2, 
      omega = aux$omega, L = seq(1, 5, by = 0.5),
      max.rl = 90, rl = c(80,85), scenario = 0, 
      ncores = 1, nboot = 100, seed = 1234)
```

### MA - Process Out of Control (scenario 1)

```{r}
x.shift = x + 0.5*(sqrt(var(x))) #mean shifted by 0.5 standard deviation
arl_ma(x.shift, mu = aux$mu, sigma2 = aux$sigma2, 
      omega = aux$omega, L = seq(1, 5, by = 0.5),
      max.rl = 90, rl = c(10,20), scenario = 1, 
      ncores = 1, nboot = 100, seed = 1234)
```

### MA statistics

```{r}
ma_statistic(x, t = 1:length(x), omega = 10)
```

### Upper and Lower Control Limits for MA

```{r}
upper_limit_ma(t = 1:length(x), omega =10, mu = aux$mu, sigma2 = aux$sigma2, L = 3)
lower_limit_ma(t = 1:length(x), omega =10, mu = aux$mu, sigma2 = aux$sigma2, L = 3)
```

## Exponential Weighted Moving Average (EWMA)

### Calculate EWMA control parameters

```{r}
aux <- control_parm_ewma(x, lambda = 0.15, max.rl = 100)
```

### EWMA - Process Under Control (scenario 0)

```{r}
arl_ewma(x, mu = aux$mu, sigma2 = aux$sigma2, 
      lambda = aux$lambda, L = seq(1, 5, by = 0.5),
      max.rl = 100, rl = c(80,85), scenario = 0, 
      ncores = 1, nboot = 100, seed = 1234)
```

### EWMA - Process Out of Control (scenario 1)

```{r}
x.shift = x + 0.5*(sqrt(var(x))) #mean shifted by 0.5 standard deviation
arl_ewma(x.shift, mu = aux$mu, sigma2 = aux$sigma2, 
      lambda = aux$lambda, L = seq(1, 5, by = 0.5),
      max.rl = 100, rl = c(10,20), scenario = 1, 
      ncores = 1, nboot = 100, seed = 1234)
```

### EWMA statistics

```{r}
ewma_statistic(x, t = 1:length(x), lambda = 0.15, x0 = mean(x))  
```

### Upper and Lower Control Limits for EWMA

```{r}
upper_limit_ewma(t = 1:length(x), mu = aux$mu, sigma2 = aux$sigma2, L = 3)
lower_limit_ewma(t = 1:length(x), mu = aux$mu, sigma2 = aux$sigma2, L = 3)
```

